Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-13 paper/ijcai16.tex
paper: refine methods and experiments a bit, still unfinished.

\paragraph{Setting.} We assume to have a multi-attribute feature space $\calX$
of configurations $\vx = (x_1, \ldots, x_n)$ over $n$ features. For the time
being we will focus on binary features only, i.e. $x_z\in\{0,1\}$, to keep
matters simple. This is a common choice for preference elicitation methods,
e.g.~\cite{guo2010real,viappiani2010optimal}; discrete features are handled by
means of a simple one-hot encoding. Partial support for continuous features
will be discussed later on.
We further assume that the set of {\em feasible} configurations is expressed as
a conjunction of linear constraints. This is not a severe restriction:
arbitrary propositional constraints can be trivially encoded in this setting,
e.g. the ``Boolean disjunction'' of two binary variables $x_1 \lor x_2$ can be
rewritten as $x_1 + x_2 \ge 1$. The full set of feasible configurations will be
indicated as $\calX_\text{feasible}$.

In adherence to previous work~\cite{guo2010real,viappiani2010optimal}, we model users by means
of linear utility functions: the user's preferences are represented by a weight
vector $\vw\in\bbR^n$, and the utility of a configuration $\vx$ is given by
$\langle \vw, \vx \rangle = \sum_{z=1}^n w_z x_z$. In the following we will
require all weights to be {\em non-negative} and {\em bounded}: the individual
weights $w_z$ must fall in a (constant but otherwise arbitrary) interval
$[w^\bot_z, w^\top_z]$. Both requirements are quite natural, and enable the
translation of our core optimization problem into a mixed-integer linear
problem (as done in Section~\ref{sec:formulation}).

During learning, the actual weight vector $\vw$ is {\em unknown} to the
learning system, and must be estimated from pairwise choices elicited from the
user. The set of examples consists of pairwise comparisons between a more
preferred configuration $\vy_+$ and a less preferred on $\vy_-$. Each preference
induces a ranking constraint $\langle \vw, \vy_+ - \vy_- \rangle \ge 0$.
\stefano{add indifference}
Details on the actual query selection strategy used will be provided in
Section~\ref{sec:querystrategy}.

@@

In the set-margin approach, the goal is twofold. First, for any given set size
$k\geq 1$, we want to find a {\em set} of $k$ weight vectors $\vw^{1},
\ldots, \vw^{k}$, chosen so that all preferences (examples) are satisfied by
the largest possible margin. This is achieved by translating all binary
preferences into inequalities of the form $\langle \vw, \vy_+ - \vy_- \rangle
\geq M$, and maximizing the margin $M$. Non-separable datasets, which occur in
practice due to user inconsistency, are handled by introducing slack variables.
Our reasoning is summarized by the following constraint:
%
$$ \langle \vw^{i}, \vy^{h}_+ - \vy^{h}_- \rangle \ge M - \varepsilon^{i}_h $$
%
where $\varepsilon^{i}_h$ is the penalty incurred by weight vector
$\vw^{i}$ for violating the ranking of example $h$.

Second, we want to produce a set of $k$ configurations $\vx^{1}, \ldots,
\vx^{k}$, so that each configuration $\vx^{i}$ is the ``best'' possible
option when evaluated according to the corresponding $\vw^{i}$. Ideally,
this requirement would be implemented as:
%
$$ \vx^{i} = \argmax_{\vx \in \calX_\text{feasible}} \langle \vw^{i}, \vx^{i} \rangle $$
%
However this formulation is highly impractical. We therefore only require 
each option $\vx^{i}$ to be the best {\em among} the various
$\vx^{1}, \ldots, \vx^{k}$. This can be accomplished by imposing
constraints of the form $\langle \vw^{i}, \vx^{i} - \vx^{j} \rangle \geq M$
for all $i,j\in[k]$, $i \ne j$.
This however does not guarantee that the $\vx^{i}$ have a high utility in
absolute terms. We therefore favor high-quality configurations by introducing
an additional term $\sum_{i=1}^k \langle \vw^{i}, \vx^{i} \rangle$ in the
objective function. \stefano{sparsity}

A straightforward encoding of the above desiderata leads to the following {\em
non-linear} optimization problem over the variables $M$, $\{ \vw^i \}$, $\{ \vx^i \}$:
%
{\footnotesize
\begin{align}
    \max
        & \;\; M - \alpha \sum_{i=1}^k \| \veps^{i} \|_1 - \beta \sum_{i=1}^k \| \vw^{i} \|_1 + \gamma \sum_{i=1}^k \langle \vw^{i}, \vx^{i} \rangle
        \nonumber
    \\
    \text{s.t.}
        & \;\; \forall \; i \in [k], \forall \; h \in [n] \nonumber
    \\
        & \;\; \qquad \langle \vw^{i}, \vy^{h}_+ - \vy^{h}_- \rangle \ge M - \varepsilon^{i}_h \label{eq:wyconstr}
    \\
        & \;\; \forall \; i, j \in [k], i \neq j \;.\; \langle \vw^{i}, \vx^{i} - \vx^{j} \rangle \ge M \label{eq:wxconstr}
    \\
        & \;\; \forall \; i \in [k] \;.\; \vw^\bot \le \vw^{i} \le \vw^\top \label{eq:wbounds}
    \\
        & \;\; \forall \; i \in [k] \;.\; \vx^{i} \in \calX_{\text{feasible}} \label{eq:xbounds}
    \\
        & \;\; \forall \; i \in [k] \;.\; \veps^{i} \ge 0 \nonumber
    \\
        & \;\; M \ge 0 \nonumber
\end{align}
}
%
Let us illustrate the above piece by piece. The objective is composed of four
parts: we want to maximize the shared margin $M$ (first part) and minimize the
total sum of the ranking errors incurred by each weight vector $\vw^{i}$
(second part), while at the same time promoting sparsity of the individual
weight vectors (third part) and quality of the configurations $\vx^{i}$ (last
part). The non-negative hyperparameters $\alpha,\beta,\gamma$ control the
influence of the various components.

The two major constraints are Eq~\ref{eq:wyconstr} and Eq~\ref{eq:wxconstr}.
The former enforces the correct ranking of the observed user preferences, while
the latter enforces the correct ranking among the generated configurations.
\stefano{WRITEME}

Equations \ref{eq:wbounds} and \ref{eq:xbounds} ensure that the obtained weight
vectors and generated configurations are in fact feasible, while the remaining
two guarantee the non-negativity of the slack and margin variables.  The
non-negativity of the $\vw^{i}$'s can be subsumed by Eq~\ref{eq:wbounds}
by choosing $\vw^\bot \ge 0$.

Note that we are choosing the options $\vx^{1}, \ldots, \vx^{k}$ and the
weight vectors $\vw^{1}, \ldots, \vw^{k}$ {\em simultaneously}. Since we
maximize the margin $M$, the optimizer will prefer a set of outcomes
$\vx^{i}$ that partition the weight space roughly equally, and corresponding
utility functions such that each $\vw^{i}$ lies (intuitively) close to the
centre of each subregion. See Figure~\ref{fig:setmargin} for a depiction of
this intuition.

@@

In order to do so, we introduce a set of fresh variables $p^{i,j}_z$ for every
$i,j\in[k]$ and $z\in[n]$. Each $p^{i,j}_z$ is enforced to be equal to the
product $w^{i}_z x^{i}_z$ through additional constraints. Assuming for the
time being these constraints to be already in place, we rewrite the fourth
component of the objective function in terms of the new variables as:
%
$$ \gamma \sum_{i=1}^k \sum_{z=1}^n p^{i,i}_z $$
%
and, similarly, Eq~\ref{eq:wxconstr} as:
%
\[ \forall \; i, j \in [k], i \neq j \;.\; \sum_{z=1}^n p^{i,i}_z - p^{i,j}_z \ge M \label{eq:pxconstr} \]
%
The fact that $p^{i,j}_z$ takes the value $w^{i}_z x^{i}_z$ is achieved by
setting the following additional constraints. We distinguish between two cases:
(i) $p^{i,i}_z$, and (ii) $p^{i,j}_z$ for $i \ne j$.  Recall that we are
maximizing the margin $M$. Now, due to Eq~\ref{eq:pxconstr}, the optimizer will
try to keep $p^{i,i}_z$ as large as possible and $p^{i,j}_z$ as small as
possible. \stefano{this is not necessarily the case, $M$ is bounded by the
$y$'s as well.}

(Case i) We add an explicit upper bound:
%
$$ p^{i,i}_z \le \min \{ w_\text{max} x^{i}_z, w^{i}_z \} $$
%
where $w_\text{max}$ is a sufficiently large constant.
On one hand, if $x^i_z = 0$ the product $w^i_z x^i_z$ evaluates to $0$, and so does
$p^{i,i}_z \le w_\text{max} x^{i}_z = 0$. On the other hand, if $x^i_z=1$
then the product $w^i_z x^i_z$ amounts to $w^i_z$. In this case, the upper
bound evaluates to $\min \{ w_\text{max}, w^{i}_z \}$. By taking a sufficiently
large constant $w_\text{max}$ (e.g. $w_\text{max} := \max_z w^\top_z$) the upper bound
boils down to $w^i_z$. Since $p^{i,i}_z$ is being maximized, it will attain the
upper bound, and thus evaluate to $w^i_z x^i_z$.

(Case ii) We add an explicit lower bound:
%
$$ p^{i,j}_z \ge \max \{ 0, w^{i}_z - w_\text{max}(1 - x^{j}_z) \} $$
%
If $x^i_z = 1$ the lower bound simplifies to $\max \{ 0, w^{i}_z \} = w^{i}_z$,
due to the non-negativity of $w^i_z$, as expected. Otherwise, if $x^i_z = 0$
then the lower bound becomes $\max \{ 0, w^{i}_z - w_\text{max} \}$, where
the second term is at most $0$. Since $p^{i,j}_z$ is being minimized, in both
cases it will attain the lower bound, and hence equate to $w^i_z x^i_z$.

Substituting the above MILP constraints into the original optimization problem,
we obtain:
{\footnotesize
\begin{align}
    \max
        & \;\; M - \alpha \sum_{i=1}^k \| \veps^{i} \|_1 - \beta \sum_{i=1}^k \| \vw^{i} \|_1 + \gamma \sum_{i=1}^k \sum_{z=1}^n p^{i,i}_z
        \nonumber
    \\
    \text{s.t.}
        & \;\; \forall \; i \in [k], \forall \; h \in [n] \nonumber
    \\
        & \;\; \qquad \langle \vw^{i}, \vy^{h}_+ - \vy^{h}_- \rangle \ge M - \varepsilon^{i}_h \nonumber
    \\
        & \;\; \forall \; i, j \in [k], i \neq j \;.\; \sum_{z=1}^n p^{i,i}_z - p^{i,j}_z \ge M
    \\
        & \;\; \forall \; i \in [k], \forall \; z \in [n] \nonumber
    \\
        & \;\; \qquad p^{i,i}_z \le \min \{ w_\text{max} x^{i}_z, w^{i}_z \}
    \\
        & \;\; \forall \; i, j \in [k], i \neq j \nonumber
    \\
        & \;\; \qquad p^{i,j}_z \ge \max \{ 0, w^{i}_z - w_\text{max}(1 - x^{j}_z) \}
    \\
        & \;\; \forall \; i \in [k] \;.\; \vw^\bot \le \vw^{i} \le \vw^\top \nonumber
    \\
        & \;\; \forall \; i \in [k] \;.\; \vx^{i} \in \calX_{\text{feasible}} \nonumber
    \\
        & \;\; \forall \; i \in [k] \;.\; \veps^{i}_h \ge 0 \nonumber
    \\
        & \;\; M \ge 0 \nonumber
\end{align}

}

@@

\paragraph{Generalization to real variables.} \stefano{WRITEME}

@@

In this section we provide an experimental evaluation of the {\sc SetMargin}
algorithm. We compare the against two strong Bayesian baselines:
\cite{guo2010real} and \cite{viappiani2010optimal}.

\stefano{describe the baselines}

We implemented the {\sc SetMargin} algorithm using Python, while the MILP
problems were solved with Gurobi 6.5.0. The full source of the experiments is
available at \stefano{add URL}.

@@

\paragraph{Synthetic Dataset.} Following the experimental protocol
in~\cite{guo2010real} and \cite{viappiani2010optimal}, in the first experiment
we evaluate the behavior of the proposed method in a challenging artificial
setting. We developed seven synthetic datasets: each dataset involves
$n=2,\ldots,7$ attributes, where each attribute takes one of $n$ possible
values. More explicitly, for $n=2$ the synthetic dataset is
$\calX_\text{feasible} = [2] \times [2]$, for $n=3$ to $\calX_\text{feasible} =
[3] \times [3] \times [3]$, and so on. The cardinality of
$\calX_\text{feasible}$ is $n^n$, and grows (super-)exponentially with $n$. For
$n=3$, the dataset is comparable to the synthetic one used
in~\cite{guo2010real} and~\cite{viappiani2010optimal} (which have three domains
of size of 2, 2 and 5, respectively, for a total of 20 feasible
configurations), while for larger $n$ it grows much larger than those typically
used in the Bayesian preference elicitation literature, and as such represents
a good test bed for comparing the scalability of the various methods.

The integer attributes were binarized using a standard one-hot encoding. The
feasible configuration space was encoded in {\sc SetMargin} through appropriate
MILP constraints (namely, mutual exclusivity of all binary variables
corresponding to each attribute, to enforce the one-hot encoding), while the
other methods required all datasets to be explicitly grounded.

The user weight vectors were sampled from four different distributions to
simulated different kinds of users. The first two were chosen as
in~\cite{guo2010real}: a uniform distribution over $[0, 100]$ and a normal
distribution with mean $25$ and variance $\frac{25}{3}$. In order to assess our
method in a truly sparse setting, we obtained a set of sparse normal and
uniform weight vectors by randomly deleting $80\%$ of the non-zero entries from
the already sampled vectors. We will refer to the four settings as {\sc
normal}, {\sc uniform}, {\sc sparse\_normal} and {\sc sparse\_uniform}. We
sampled a total of $100$ weight vectors for each setting. All methods were
evaluated on the very same weight vectors.

>>>>

\paragraph{Setting.} We assume to have a multi-attribute feature space $\calX$
of configurations $\vx = (x_1, \ldots, x_n)$ over $n$ features. For the time
being we will focus on binary features only, i.e. $x_z\in\{0,1\}$, to keep
matters simple. This is a common choice for preference elicitation methods,
e.g.~\cite{guo2010real,viappiani2010optimal}; discrete features are handled by
means of a simple one-hot encoding. Partial support for continuous features
will be discussed later on.

We further assume that the set of {\em feasible} configurations is expressed as
a conjunction of linear constraints. This is not a severe restriction:
arbitrary propositional constraints can be trivially encoded in this setting,
e.g. the ``Boolean disjunction'' of two binary variables $x_1 \lor x_2$ can be
rewritten as $x_1 + x_2 \ge 1$. The full set of feasible configurations will be
indicated as $\calX_\text{feasible}$.

In adherence to previous work~\cite{guo2010real,viappiani2010optimal}, we model users by means
of linear utility functions: the user's preferences are represented by a weight
vector $\vw\in\bbR^n$, and the utility of a configuration $\vx$ is given by
$\langle \vw, \vx \rangle = \sum_{z=1}^n w_z x_z$. In the following we will
require all weights to be {\em non-negative} and {\em bounded}: the individual
weights $w_z$ must fall in a (constant but otherwise arbitrary) interval
$[w^\bot_z, w^\top_z]$, with $w^\bot_z \ge 0$. Both requirements are quite
natural, and enable the translation of our core optimization problem into a
mixed-integer linear problem (as done in Section~\ref{sec:formulation}).

During learning, the actual weight vector $\vw$ is {\em unknown} to the
learning system, and must be estimated from pairwise choices elicited from the
user. The set of examples consists of pairwise comparisons between a more
preferred configuration $\vy_+$ and a less preferred on $\vy_-$. Each preference
induces a ranking constraint $\langle \vw, \vy_+ - \vy_- \rangle \ge 0$.
Details on the actual query selection strategy will be provided in
Section~\ref{sec:querystrategy}.
\stefano{add indifference}

@@

In the set-margin approach, the goal is twofold. First, for any given set size
$k\geq 1$, we want to find a {\em set} of $k$ weight vectors $\vw^{1},
\ldots, \vw^{k}$, chosen so that all preferences (examples) are satisfied by
the largest possible margin. This is achieved by translating all binary
preferences into inequalities of the form $\langle \vw^i, \vy^h_+ - \vy^h_- \rangle
\geq M$, where $h$ ranges over the examples, and maximizing the margin $M$.
Non-separable datasets, which occur in practice due to user inconsistency, are
handled by introducing slack variables. The updated constraints look as follows:
%
$$ \langle \vw^{i}, \vy^{h}_+ - \vy^{h}_- \rangle \ge M - \varepsilon^{i}_h $$
%
where $\varepsilon^{i}_h$ is the penalty incurred by weight vector $\vw^{i}$
for violating the ranking of example $h$.

Second, we want to produce a set of $k$ configurations $\vx^{1}, \ldots,
\vx^{k}$, so that each configuration $\vx^{i}$ is the ``best'' possible
option when evaluated according to the corresponding $\vw^{i}$. Ideally,
this requirement would be implemented as:
%
$$ \vx^{i} = \argmax_{\vx \in \calX_\text{feasible}} \langle \vw^{i}, \vx^{i} \rangle $$
%
However this formulation is highly impractical. We therefore only require 
each option $\vx^{i}$ to be the best {\em among} the configurations
$\{ \vx^i \}$. This can be accomplished by imposing
constraints of the form $\langle \vw^{i}, \vx^{i} - \vx^{j} \rangle \geq M$
for all $i,j\in[k]$, $i \ne j$.
This however does not guarantee that the produced $\{ \vx^{i} \}$ have a high
{\em absolute} utility. We therefore favor high-quality configurations by
introducing an additional term $\sum_{i=1}^k \langle \vw^{i}, \vx^{i} \rangle$
in the objective function.

A straightforward encoding of the above desiderata leads to the following {\em
non-linear} optimization problem over the variables $M$, $\{ \vw^i \}$, $\{ \vx^i \}$:
%
{\footnotesize
\begin{align}
    \max
        & \;\; M - \alpha \sum_{i=1}^k \| \veps^{i} \|_1 - \beta \sum_{i=1}^k \| \vw^{i} \|_1 + \gamma \sum_{i=1}^k \langle \vw^{i}, \vx^{i} \rangle
        \nonumber
    \\
    \text{s.t.}
        & \;\; \forall \; i \in [k], \forall \; h \in [n] \nonumber
    \\
        & \;\; \qquad \langle \vw^{i}, \vy^{h}_+ - \vy^{h}_- \rangle \ge M - \varepsilon^{i}_h \label{eq:wyconstr}
    \\
        & \;\; \forall \; i, j \in [k], i \neq j \;.\; \langle \vw^{i}, \vx^{i} - \vx^{j} \rangle \ge M \label{eq:wxconstr}
    \\
        & \;\; \forall \; i \in [k] \;.\; \vw^\bot \le \vw^{i} \le \vw^\top \label{eq:wbounds}
    \\
        & \;\; \forall \; i \in [k] \;.\; \vx^{i} \in \calX_{\text{feasible}} \label{eq:xbounds}
    \\
        & \;\; \forall \; i \in [k] \;.\; \veps^{i} \ge 0 \nonumber
    \\
        & \;\; M \ge 0 \nonumber
\end{align}
}
%
Let us illustrate the above piece by piece. The objective is composed of four
parts: we maximize the shared margin $M$ (first part) and minimize the total
sum of the ranking errors $\veps^i$ incurred by each weight vector $\vw^{i}$
(second part), while at the same time regularizing the magnitude of the
weights (third part) and quality of the configurations $\{ \vx^{i} \}$ (last
part). The non-negative hyperparameters $\alpha,\beta,\gamma$ control the
influence of the various components.

The third part requires requires some further explanation. We choose an
$\ell_1$ regularizer in order to facilitate learning {\em sparse} weight
vectors: it is reasonable to assume that a user will have strong opinions
over some attributes, but will be indifferent over most of them.
\stefano{Andrea, improve the above please}

The two core constraints as Equations~\ref{eq:wyconstr} and \ref{eq:wxconstr},
which are taken directly from the discussion above. The former enforces the
correct ranking of the observed user preferences, while the latter ensures that
the generated configurations are ranked correctly with respect to the
corresponding weight vectors. Equations \ref{eq:wbounds} and \ref{eq:xbounds}
ensure that the weights and configurations are in fact feasible, while the
remaining two guarantee the non-negativity of the slack and margin variables.
Since we require $\vw^\bot \ge 0$, Eq.~\ref{eq:wbounds} also enforces the
weights to be non-negative.

Note that we are choosing the options $\{ \vx^i \}$ and the weight vectors $\{
\vw^i \}$ {\em simultaneously}. Since we maximize the margin $M$, the optimizer
will prefer a set of outcomes $\{ \vx^{i} \}$ that partition the weight space
roughly equally, and corresponding utility functions such that each $\vw^{i}$
lies (intuitively) close to the centre of each subregion. See
Figure~\ref{fig:setmargin} for a depiction of this intuition.

@@

In order to do so, we introduce a set of fresh variables $p^{i,j}_z$ for every
$i,j\in[k]$ and $z\in[n]$. Assuming for the time being that the new variables
do satisfy the equation $p^{i,j}_z = w^i_z x^i_z$, we rewrite the fourth
component of the objective function in terms of the new variables as:
%
$$ \gamma \sum_{i=1}^k \sum_{z=1}^n p^{i,i}_z $$
%
and, similarly, Eq~\ref{eq:wxconstr} as:
%
\[ \forall \; i, j \in [k], i \neq j \;.\; \sum_{z=1}^n p^{i,i}_z - p^{i,j}_z \ge M \label{eq:pxconstr} \]
%
The fact that $p^{i,j}_z = w^{i}_z x^{i}_z$ is achieved by
setting the following additional constraints. We distinguish between two cases:
(i) $p^{i,i}_z$, and (ii) $p^{i,j}_z$ for $i \ne j$.  Recall that we are
maximizing the margin $M$. Now, due to Eq~\ref{eq:pxconstr}, the optimizer will
try to keep $p^{i,i}_z$ as large as possible and $p^{i,j}_z$ as small as
possible. \stefano{this is not necessarily the case, $M$ is bounded by the
$y$'s as well.}

(Case i) We add an explicit upper bound:
%
$$ p^{i,i}_z \le \min \{ w_\text{max} x^{i}_z, w^{i}_z \} $$
%
where $w_\text{max}$ is a sufficiently large constant.
On one hand, if $x^i_z = 0$ the product $w^i_z x^i_z$ evaluates to $0$, and so does
the upper bound $w_\text{max} x^{i}_z = 0$. On the other hand, if $x^i_z=1$
then the product $w^i_z x^i_z$ amounts to $w^i_z$, while the upper
bound reduces to $\min \{ w_\text{max}, w^{i}_z \}$. By taking a sufficiently
large constant $w_\text{max}$ (e.g. $w_\text{max} := \max_z w^\top_z$) the
upper bound simplifies to $w^i_z$. Since $p^{i,i}_z$ is being maximized, in
both cases it will attain the upper bound, and thus satisfy $p^{i,j}_z = w^i_z x^i_z$.

(Case ii) We add an explicit lower bound:
%
$$ p^{i,j}_z \ge \max \{ 0, w^{i}_z - w_\text{max}(1 - x^{j}_z) \} $$
%
If $x^i_z = 1$ the lower bound simplifies to $\max \{ 0, w^{i}_z \} = w^{i}_z$,
due to the non-negativity of $w^i_z$. Otherwise, if $x^i_z = 0$
then the lower bound becomes $\max \{ 0, w^{i}_z - w_\text{max} \}$, where
the second term is at most $0$. Since $p^{i,j}_z$ is being minimized, in both
cases it will attain the lower bound, and thus satisfy $p^{i,j}_z = w^i_z x^i_z$.

Substituting the above MILP constraints into the original non-linear
formulation, we obtain the following mixed-integer linear problem:
%
{\footnotesize
\begin{align}
    \max
        & \;\; M - \alpha \sum_{i=1}^k \| \veps^{i} \|_1 - \beta \sum_{i=1}^k \| \vw^{i} \|_1 + \gamma \sum_{i=1}^k \sum_{z=1}^n p^{i,i}_z
        \nonumber
    \\
    \text{s.t.}
        & \;\; \forall \; i \in [k], \forall \; h \in [n] \nonumber
    \\
        & \;\; \qquad \langle \vw^{i}, \vy^{h}_+ - \vy^{h}_- \rangle \ge M - \varepsilon^{i}_h \nonumber
    \\
        & \;\; \forall \; i, j \in [k], i \neq j \;.\; \sum_{z=1}^n p^{i,i}_z - p^{i,j}_z \ge M
    \\
        & \;\; \forall \; i \in [k], \forall \; z \in [n] \nonumber
    \\
        & \;\; \qquad p^{i,i}_z \le \min \{ w_\text{max} x^{i}_z, w^{i}_z \}
    \\
        & \;\; \forall \; i, j \in [k], i \neq j \nonumber
    \\
        & \;\; \qquad p^{i,j}_z \ge \max \{ 0, w^{i}_z - w_\text{max}(1 - x^{j}_z) \}
    \\
        & \;\; \forall \; i \in [k] \;.\; \vw^\bot \le \vw^{i} \le \vw^\top \nonumber
    \\
        & \;\; \forall \; i \in [k] \;.\; \vx^{i} \in \calX_{\text{feasible}} \nonumber
    \\
        & \;\; \forall \; i \in [k] \;.\; \veps^{i}_h \ge 0 \nonumber
    \\
        & \;\; M \ge 0 \nonumber
\end{align}
}
%
which can be solved by any suitable MILP solver.

@@

The simplest alternative is to query the user $\frac{1}{2}n(n-1)$ pairs.

\paragraph{Generalization to real variables.}

@@

In this section we provide extensive experimental evaluation of the {\sc
SetMargin} algorithm. We implemented the {\sc SetMargin} algorithm using
Python, and leverage Gurobi 6.5.0 for solving the MILP problem. Both the 
{\sc SetMargin} source code and the full experimental setup are available at
\stefano{add URL}.

We compare {\sc SetMargin} against two strong Bayesian baselines:
\cite{guo2010real} and \cite{viappiani2010optimal}.
\stefano{Paolo, could you describe the baselines?}

We adopted the {\em indifference-augmented} Bradley-Torr user response model
introduced in~\cite{guo2010real}. When queried about a pair of configurations,
the user replies with the true utility of the two items. According to the
classical Bradley-Torr model, which does not attempt to model {\em indifference},
the proabability that a user $\vw$ will prefer configuration $\vx^i$ over
the alternative $\vx^j$, barring indifference, amounts to:
%
$$ P(\vx^i > \vx^j \;|\; \vw, \vx^i \not\sim \vx^j) = (1 + \exp(-\alpha \langle\vw,\vx^i - \vx^j\rangle))^{-1} $$
%
In other words, the probability grows with the difference between the utilities
of the two items. Support for indifference has been introduced
in~\cite{guo2010real} by postulating that the probability of the user being
indifferent about the two configurations $\vx^i, \vx^j$ depends on how close
the two utilities are, as in:
%
$$ P(\vx^i \sim \vx^j \;|\; \vw) = \exp(\beta |\langle\vw,\vx^i - \vx^j\rangle|) $$
%
The parameters $\alpha$ and $\beta$ were set as in~\cite{guo2010real}. Please
see the latter for more details
\stefano{The above does not satisfy me at all.}

@@

\paragraph{Synthetic Dataset.} Following the experimental protocol
in~\cite{guo2010real} and \cite{viappiani2010optimal}, in the first experiment
we evaluate the behavior of the proposed method in a challenging artificial
setting. We developed seven synthetic datasets: each dataset involves
$n=2,\ldots,7$ attributes, where each attribute takes one of $n$ possible
values. More explicitly, for $n=2$ the synthetic dataset is
$\calX_\text{feasible} = [2] \times [2]$, for $n=3$ to $\calX_\text{feasible} =
[3] \times [3] \times [3]$, and so on. The cardinality of
$\calX_\text{feasible}$ is $n^n$, and grows (super-)exponentially with $n$. For
$n=3$, the dataset is comparable to the synthetic one used
in~\cite{guo2010real} and~\cite{viappiani2010optimal} (which have three domains
of size of 2, 2 and 5, respectively, for a total of 20 feasible
configurations), while for larger $n$ it grows much larger than those typically
used in the Bayesian preference elicitation literature, and as such represents
a good test bed for comparing the scalability of the various methods.
The feasible configuration space was encoded in {\sc SetMargin} through
appropriate MILP constraints, while the other methods required all datasets to
be explicitly grounded.

Users were simulated by drawing random utility vectors from four different
distributions. The first two mimic those used in~\cite{guo2010real}: (1) a
uniform distribution over $[1, 100]$ for each individual weight, and (2) a
normal distribution with mean $25$ and covariance $\frac{25}{3}$\footnote{This
procedure differs from the one reported in~\cite{guo2010real}; we opted for
following the procedure implemented in their code. \stefano{more diplomacy needed}}.
We further produced two novel {\em sparse} sets of weight vectors by deleting
$80\%$ uniformly at random \stefano{Paolo, double check please} the entries
from the vectors sampled in the uniform and normal settings. We sampled $100$
vectors for each setting. All methods were evaluated on the very same weight
vectors.
